\name: Deterministic and Coherent Implicits

### 2018-06-19 jfp/src/DesignChoices.tex
Section 3

\section{Design Choices}

Before diving into the technical details, we wish to discuss and justify a number of design 
choices taken in \name. Mostly, many of these choices are motivated by the design of Haskell 
type classes or Scala implicits.

@@

A few concerns are:

1) open vs closed world. In open world you could add more instances, so you don't know whether your choice is unique or the best
2) reasoning: if you backtrack then programmers have to follow the backtracking reasoning, which can be complex for more involved instance declarations
3) performance: You may pay significant penalties at compile time by backtracking

@@

special treatment of superclasses:

compute the closure of all given superclasses before resolution

-> treat that closure like other givens

 when matching, try to match the givens first, because they are non-recursive

-> if none of the givens work, try global instances

>>>>

\section{Discussion}

In the design of \name we had to take several design decisions. In
this section we discuss and justify several of those design decisions.
Mostly, many of these choices are motivated by the design of Haskell 
type classes or Scala implicits.

@@

@@
